The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

Also, as self-confidence is considered to rely partly on one’s integration within social networks (OECD Report 2009), we will also refer to cross-cultural studies such as that of Green, Deschamps and Páez (2005) about individualism and collectivism, or what Freeman (1997) called idiocentrism and allocentrism. Raeff, Greenfield and Quiroz (2000) have also conceptualised interpersonal relationships in both cultural contexts. More school-focused, Yamauchi (1998) as well as Davies and Aurini (2003) have looked at individualism and collectivism in the classroom and in pedagogy respectively. All these will be precious on the way.

Besides direct or indirect school effects, we will necessarily look into entrepreneurship and its determinants at large. Thus we will refer to Grilo and Thurik’s research (2005 and 2006) about what determines entrepreneurship engagement levels throughout the European Union, and also to Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries (2002). Eventtually, with Gartner (1990) we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper (2008), we will asks ourselves what “entrepreneurship” data really shows.

>>>>

Also, as self-confidence is considered to rely partly on one’s integration within social networks (OECD Report 2009), we will refer to cross-cultural studies such as that of Green, Deschamps and Páez (2005) about individualism and collectivism, what Freeman (1997) called idiocentrism and allocentrism. Raeff, Greenfield and Quiroz (2000) have also conceptualised interpersonal relationships in both contexts. More school-focused, Yamauchi (1998) as well as Davies and Aurini (2003) have looked at individualism and collectivism in the classroom and in pedagogy respectively. All these will be precious on the way.

Besides direct or indirect school effects, we will necessarily look into entrepreneurship and its determinants at large. Thus we will quote Grilo and Thurik’s research (2005 and 2006) about what determines entrepreneurship engagement levels throughout the European Union, and also Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries (2002). Eventually, with Gartner (1990) we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper (2008), we will ask ourselves what “entrepreneurship” data really shows.
